Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 bckground.tex
minor tweaks.

\jhanote{In this section we should talk less about PanDA and more about other
WMS -- highlighting the fact that (i) there isn't a comprehensive systems
(design, architecture and execution properties) discussion of other WMS so
difficult to compare}\mtnote{Better?}
\jhanote{(ii) real comparison should be to the Gliden-in WMS ecosystem and use
this as opportunity to narrate the reasons for the divergence.}\mtnote{From our
meetings with Sergey: Before Run 1, ATLAS management become uncomfortable with
the pace at which other WMS were being developed, loosing trust in their ability
to deliver production-grade capabilities. ATLAS USA decided to go solo and
developed their own solution. PanDA proven to be able to deliver the
usual pilot-based WMS capabilities at the right scale. For that, it was chosen
over other solutions.}
\jhanote{Also might this section be moved towards the rear, as this is  a
practice paper and not a traditional research paper?}\mtnote{Done.}

>>>>

% \jhanote{In this section we should talk less about PanDA and more about other
% WMS -- highlighting the fact that (i) there isn't a comprehensive systems
% (design, architecture and execution properties) discussion of other WMS so
% difficult to compare}\mtnote{Better?}

\jhanote{(ii) real comparison should be to the Gliden-in WMS ecosystem and use
this as opportunity to narrate the reasons for the divergence.}\mtnote{From our
meetings with Sergey: Before Run 1, ATLAS management become uncomfortable with
the pace at which other WMS were being developed, loosing trust in their ability
to deliver production-grade capabilities. ATLAS USA decided to go solo and
developed their own solution. PanDA proven to be able to deliver the
usual pilot-based WMS capabilities at the right scale. For that, it was chosen
over other solutions.}

% \jhanote{Also might this section be moved towards the rear, as this is  a
% practice paper and not a traditional research paper?}\mtnote{Done.}
